How to reduce Item Nonresponse in Face-to-Face Surveys? A Review and Evidence from the European Social Survey

### 2024-02-06 inr_ESS9_text.tex
de-anonymised version after reviews

%opening
\title{How to reduce Item Nonresponse in Face-to-Face Surveys? A Review and Evidence from the European Social Survey}
%\author{Malte Grönemann \\ University of Mannheim, Mannheim, Germany}

@@

More information on the data, variables, summary statistics, all of the code used for preparation and analysis, and discussions on missing values and model specification are available in the  %\href{https://doi.org/10.17605/OSF.IO/M83GY}
{supplemental material} [OSF LINK HIDDEN FOR REVIEW].

@@

[HIDDEN FOR REVIEW]

%I want to thank Achim Koch, Johanna Mehltretter and especially Tobias Gummer for helpful comments in multiple stages of this project. I want to thank Marcel Kappes and Thomas Gautschi for methodological discussions.

%This work was supported by the University of Mannheim’s Graduate School of Economic and Social Sciences.

>>>>

%opening
\title{How to reduce Item Nonresponse in Face-to-Face Surveys? A Review and Evidence from the European Social Survey}
\author{Malte Grönemann \\ University of Mannheim, Mannheim, Germany}

@@

More information on the data, variables, summary statistics, all of the code used for preparation and analysis, and discussions on missing values and model specification are available in the  \href{https://doi.org/10.17605/OSF.IO/M83GY}{supplemental material}.

@@

I want to thank Achim Koch, Johanna Mehltretter and especially Tobias Gummer for helpful comments in multiple stages of this project. I want to thank Marcel Kappes and Thomas Gautschi for methodological discussions.

This work was supported by the University of Mannheim’s Graduate School of Economic and Social Sciences.
